### 2020-02-14 README.Rmd
Updating

>>>>

### Inadvisable workflow

*NOTE: This workflow is not recommended!*

This workflow violates the "validation first" principle. You can supply the `target_value` at the creation of oolong test.

```{r}
dfm(trump2k, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(trump2k, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> trump2k_afinn_score
oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive", target_value = trump2k_afinn_score)
oolong_test
```

```{r, include = FALSE}
oolong_test$.__enclos_env__$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
```

```{r}
oolong_test$lock()
oolong_test$
```
